---
title: "Day Care Fines"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
    keep_md: true
---

<script type="text/javascript">
 function showhide(id) {
    var e = document.getElementById(id);
    e.style.display = (e.style.display == 'block') ? 'none' : 'block';
 }
</script>

```{r, include=FALSE}
library(mosaic)
library(DT)
library(pander)
library(car)
library(plyr)

# To get the "late" dataset into your R Console, 
# you need to go to your file menu of R-Studio and select
# "Session, Set working directory, To source file location"
# Then click the green "play" arrow in 
# the top right corner of this gray R-Chunk. 
late <- read.csv("../Data/late.csv", header=TRUE)
# Then type:
# > View(late)
# in your R Console
```






## Background {.tabset .tabset-fade}

### Overview
<!-- Be sure to add your own background here before beginning the Analysis. -->

Ten day-cares in Isreal participated in a policy experiment with parents who are late picking up their children. Six of the day-cares imposed a fine for 14 weeks. The other four day-cares were used as a conrol group. (See the Study Details tab for more details)

This analysis investigates the results.

<!--End your background before here.-->
<!--Click the little black arrow to 
the left to expand/hide these next sections.-->
### Study Details

<div style="color:#a8a8a8;">
This background is quoted directly from the article ["A Fine is a Price"](http://rady.ucsd.edu/faculty/directory/gneezy/pub/docs/fine.pdf). 
</div>

<div style="padding-left:30px; padding-right:30px;">

There are two types of day-care centers in Israel: private and public. A study was conducted in 10 private day-care centers in the city of Haifa from January to June 1998. All of these centers are located in the same part of town, and there is no important difference among them. During the day children are organized into groups according to age, from 1 to 4 years old. Each day-care center is allowed to hold a maximum of 35 children. In some exceptional cases a few additional children are allowed. The fee for each child is NIS 1,400 per month. (The NIS is the New Israeli Shekel.) At the time of the study, a U.S. dollar was worth approximately NIS 3.68, so the fee was about $380 at that time. 

The contract signed at the beginning of the year states that the day-care
center operates between 0730 and 1600. There is no mention of what happens if parents come late to pick up their children. In particular, before the beginning of the study, there was no fine for coming late. When parents did not come on time, one of the teachers had to wait with the children concerned. Teachers would rotate in this task, which is considered part of the job of a teacher, a fact that is clearly explained when a teacher is hired. Parents rarely came after 1630. 

A natural option [to fix the problem of parents showing up late] is to introduce a fine: every time a parent comes late, [they] will have to pay a fine. Will that reduce the number of parents who come late? If the fine is removed, will things revert back to the way they were originally?

The overall period of the study was 20 weeks. In the first 4 weeks we
simply recorded the number of parents who arrived late each week. At the
beginning of the fifth week, we introduced a fine in six of the 10 day-care centers, which had been selected randomly. The announcement of the fine was made with a note posted on the bulletin board of the day-care center. Parents tend to look at this board every day, since important announcements are posted there. The announcement specified that the fine would be NIS 10 for a delay of 10 minutes or more. The fine was per child; thus, if parents had two children in the center and they came late, they had to pay NIS 20. Payment was made to the principal of the day-care center at the end of the month. Since monthly payments are made to the owner during the year, the fines were added to those amounts. The money was paid to the owner, rather then to the teacher who was staying late (and did not get any additional money). The teachers were informed of the fine but not of the study. Registering the names of parents who came late was a common practice in any case.

At the beginning of the seventeenth week, the fine was removed with no explanation. Notice of the cancellation was posted on the board. If parents asked why the fines were removed, the principals were instructed to reply that the fine had been a trial for a limited time and that the results of this trial were now being evaluated.

A comparison with other fines in Israel may give an idea of the size of
the penalty that was introduced. A fine of NIS 10 is relatively small but not insignificant. In comparison, the fine for illegal parking is NIS 75; the fine for driving through a red light is NIS 1,000 plus penalties; the fine for not collecting the droppings of a dog is NIS 360. For many of these violations, however, detection and enforcement are low or, as in the case of dog dirt, nonexistent in practice. A baby-sitter earns between NIS 15 and NIS 20 per hour. The average gross salary per month in Israel at the time of the study was NIS 5,595.

</div>


### The Data (Wide)


The `late` Day Care Center data is shown here in the "wide data format". 

```{r, out.width=300}
#Show the full width of the "Wide" version of the late data:
pander(late, split.tables = Inf)
```


### The Data (Long)

The `Late` Day Care Center data is shown here in the "long data format".

```{r}
# This code reshapes the data into "long" format called Late.
# To get the "Late" dataset into your R Console, 
# you need to click the green "play" arrow in 
# the top right corner of this gray R-Chunk. 
# Then type:
#   > View(Late)
# in your R Console
Late <- reshape(late,
                varying = paste("Week",1:20, sep=""), 
                v.names = "No.ofLateChildren",
                timevar = "Week", 
                times = 1:20, 
                idvar = "Center",
                new.row.names = 1:200,
                direction = "long")
pander(Late)
```


 
##  
<!-- You can begin writing again after here.-->



## Analysis

This first plot compares the outcomes of late children for the 4 control day-cares with the 6 fined day-cares, over the entire 20 week period:
```{r echo=F}
#revalue(Late, c("Control"="Control Group", "Fine"="Fine Group"))

Late$Period <- cut(Late$Week, c(0,4,16,20), c("Before Fine", "During Fine", "After Fine"))

xyplot(No.ofLateChildren ~ Treatment, data=Late, type=c("p","a"),  col="#00AA00", pch=18, main="Outcome Across All 20 Weeks")
```

This plot shows the outcome of late children by time (Before fine, During Fine, After Fine) for all 10 day cares, whether or not they implemented a fine:

```{r echo=F}
xyplot(No.ofLateChildren ~ Period, data=Late, type=c("p","a"), col="#D04300", pch=18, main="Outcome For Both Treatments", xlab="Time")
```

This plot compares both factors, the treatment and the time frame as they interact together:

```{r echo=F}
xyplot(No.ofLateChildren ~ Period, data=Late, groups=Treatment, type=c("p","a"), auto.key=list(corner=c(0,1)), pch=c(15,18), main="Interaction Between Treatments and Periods")
```
</br >
Having a control group allows us to see the trend which would have occured if no fine was charged. This way we know that the trend observed by the fined group is due to the fine and not some other curcumstances.

Using a two way ANOVA we can further determine if these results are not by chance. I chose to maintain a 95% confidence interval.

For the treatments ($\alpha$):
$$
H_0 : \alpha_{Control} = \alpha_{Fine} = 0
$$
$$
H_a : \alpha_i \ne 0 \text{ for at least one }i
$$
For the time periods ($\beta$):
$$
H_0 : \beta_{Before} = \beta_{During} = \beta_{After} = 0
$$
$$
H_a : \beta_j \ne 0 \text{ for at least one }j
$$
For the interaction between the treatments ($\alpha$) and the periods ($\beta$):
$$
H_0 : \text{The effect of α is the same for all levels of β}
$$
$$
H_a : \text{The effect of α is different for at least one level of β}
$$

</br>
I'll first check that the data is appropriate for the test:
```{r}
Late.aov <- aov(No.ofLateChildren ~ Treatment+Period+Treatment:Period, data=Late)
par(mfrow=c(1,2))
plot(Late.aov, which=2)
plot(Late.aov, which=1)
```
</br>The residuals are normally disrtibuted and the variance is sufficiently constant. The ANOVA will be reliable.

```{r echo=F}
pander(summary(Late.aov))
```

In fixed notation, the P-value for the interaction between time and treatments is 0.000004162. These results were not by chance.

## Interpretation

There is sufficient evidence that the fine influenced the number of late children. </br >
From the interaction graph we can see an obvious increase in late children after the fine was introduced. The number of late children did not return to lower values after the fine was removed. The fine may have allowed parents to feel that it was okay to be late because the day care was being paid for it. There could be multiple reasons that the trend remained after the fine was removed. Most likely, the parents had formed a habit of being late. It is also possible that their attitudes about leaving their kids changed after a fine was introduced and this may not be easily reversible. It would be good to continue to track the number of late children and see if any changes occur.