---
title: "Student Housing Costs"
output: 
  html_document:
    theme: readable
    code_folding: hide
    toc: true
    toc_float: false
---

```{r, include=FALSE}
library(mosaic)
library(DT) # If you get an error stating: 
            # Error in library(DT): there is no package called 'DT'
            # You will need to run: install.packages("DT") 
            # in your Console, then try "Knit HTML" again.
library(ggplot2)
Rent <- read.csv("../Data/Rent1.csv", header=TRUE)
```

<br />

## Background
Stephanie[^1] is a student that will be starting school at BYU-Idaho next semester. Here is a copy of the email request for information that she sent.

"Hi. My name is Stephanie. I would like to learn about what housing options I have for living at BYU-Idaho next semester. It will be my first semester there, so I would like to find something that is close to campus and around $300 a month in rent. I'm not too picky on roomates, but I would like somewhere that has a lot of people around so I can get to know as many people as possible. Thanks in advance!"


**My Response:**

Hello Stephanie,

I've compiled a list of approved housing for women from the [BYU-Idaho Housing Website](https://web.byui.edu/tis/search). This first table provides all results:
```{r}
womens <- subset(Rent, Gender=="F")
datatable(womens, extensions="Responsive", options=list(lengthMenu = c(3,10,30,57)))
```

The table supplied will allow you to sort the options if you click on the arrows.

Tip: Clicking "Miles2Campus"" once, and then "Cost" once will sort both low to high with cost being the first preference.

The "Miles2Campus" and suggested walking distances will give you an idea but are not all accurate.

Click the "+" buttons to view more details. It is useful to check the addresses on a map.

## Analysis
This graph shows the relationship between the prices and proximity to campus. The dots are also colored according to the number of residents.
```{r, warning=F}
#colorfade <- colorRampPalette(c("red", "green", "blue"))
#plot(Cost ~ Miles2Campus, data=Rent, col=colorfade(Rent$Residents))

ggplot(Rent, aes(y = Cost, x = Miles2Campus, col = Residents)) + geom_point() + scale_colour_gradient2("Residents", low = "#00FFBB", mid ="#0000FF", high = "#BB00FF", midpoint = 200)
```

Since you said that you were looking to pay \$300 a month, I reduced this new list to only the ones which are equivalent to $362 a month or less. I also removed any sites with a capacity of fewer than 30 residents.
```{r}
costwm <- subset(Rent, Gender=="F" & Cost<=1068.52 & Residents>=30)
datatable(costwm, extensions="Responsive", options=list(lengthMenu = c(5,13)))
```



## Interpretation

Any of the apartments may be worth your consideration. Birch Plaza is a popular choice. You might also consider Brookyln or Davenport for their price. The more expensice ones have some nice features, like Birch Wood I with its hot tub! 

[^1]: Note that Stephanie is a fictional character who is based on real experiences of many faculty and staff here at BYU-Idaho.