---
title: "*Census at School* Survey Analysis"
author: "Annonymous for Now"
date: "February 9, 2019"
output: 
  html_document:
    code_folding: "hide"
    theme: "yeti"
---

```{r setup, include=FALSE}
library(tidyverse)
library(car)
library(pander)
```

I selected 100 total samples from all states from students in grades 6-12 from *Census at School*:
https://ww2.amstat.org/censusatschool/Exports/1549761705425_DATA.csv

```{r, message = FALSE}
setwd("C:/Users/Jim/Desktop/MATH 325/Math 325 Notebook/Math_425_Project_Data")

data <- read_csv("data/1549761705425_DATA.csv") %>% 
  mutate(Outdoor_Activities_Hours = as.numeric(Outdoor_Activities_Hours)) %>% 
  replace_na(list(Hanging_Out_With_Friends_Hours = 0, Talking_On_Phone_Hours = 0, Doing_Homework_Hours = 0, Doing_Things_With_Family_Hours = 0, Outdoor_Activities_Hours = 0, Video_Games_Hours = 0, Social_Websites_Hours = 0, Texting_Messaging_Hours = 0, Computer_Use_Hours = 0, Watching_TV_Hours = 0, Paid_Work_Hours = 0, Work_At_Home_Hours = 0)) %>%
  mutate(TotalHours = Hanging_Out_With_Friends_Hours + Talking_On_Phone_Hours + Doing_Homework_Hours + Doing_Things_With_Family_Hours + Outdoor_Activities_Hours + Video_Games_Hours + Social_Websites_Hours + Texting_Messaging_Hours + Computer_Use_Hours + Watching_TV_Hours + Paid_Work_Hours + Work_At_Home_Hours) %>%
  mutate(QualityTime = (Doing_Things_With_Family_Hours + Outdoor_Activities_Hours + Paid_Work_Hours + Work_At_Home_Hours) / TotalHours, SpentTime = (Social_Websites_Hours + Texting_Messaging_Hours + Video_Games_Hours + Watching_TV_Hours) / TotalHours) %>% 
  select(TotalHours, QualityTime, SpentTime) %>% 
  filter(TotalHours != 0)

time_lm <- lm(QualityTime ~ SpentTime, dat = data)

ggplot(data, aes(x = SpentTime, y = QualityTime)) +
  geom_point() +
  geom_smooth(method = lm) +
  labs(title = "6-12th graders in the US reported relative portion of time spent each week", x = "Spent Time", y = "Quality Time")
```

I investigated if there was a correlation between the portion of time students spend on less meaningful activities

('Doing_Things_With_Family_Hours', 'Outdoor_Activities_Hours', 'Paid_Work_Hours', and 'Work_At_Home_Hours'.)

and the portion of time spent on more meaningful activities 

('Social_Websites_Hours', 'Texting_Messaging_Hours', 'Video_Games_Hours', and 'Watching_TV_Hours'). 

Because students wildly varied on their estimations of how many hours are in a given week, I divided their reported hours by the total to get a percentage of all hours. The total time was aggregated from all of these activities, which do not include everything that happens in a day, like sleeping: 

'Hanging_Out_With_Friends_Hours', 'Talking_On_Phone_Hours', 'Doing_Homework_Hours', 'Doing_Things_With_Family_Hours', 

'Outdoor_Activities_Hours', 'Video_Games_Hours', 'Social_Websites_Hours', 'Texting_Messaging_Hours', 

'Computer_Use_Hours', 'Watching_TV_Hours', 'Paid_Work_Hours', 'Work_At_Home_Hours' <br/><br/>


It is important to note that I replaced all missing values with zeros. This is logical in some cases (e.g. A student doesn't include a number if it was zero), but clearly misrepresentative for others (e.g. A student started filling out numbers but stopped midway). After aggregating, the model does not include any rows where the total hours reported is zero; there is only one instance where the total hours were 12, but the 'SpentTime' and 'QualityTime' hours were both reported as 0 and that one has been kept. After dropping rows there are 85 remaining, and a resulting 83 degrees of freedom for the linear regression. <br/><br/>

I used the following hypothesis statements for a simple linear regression:
$$
H_0: \beta_0 = 0 \\
H_0: \beta_1 = 0 \\
H_a: \beta_0 \ne 0 \\
H_a: \beta_1 \ne 0 \\
\alpha = 0.05
$$
It would be surprising if either null hypothesis was not rejected. These are the results of the analysis:

```{r}
pander(summary(time_lm))
```

$$
\underbrace{\hat{Y}_i}_\text{Quality Time} = 0.4523 - 0.5912 \times \underbrace{X_i}_\text{Spent Time}
$$

Both null hypotheses should be rejected. The intercept value is meaningful in this case, because I can observe that students who spend no time in the less valuable activities listed spend an average of 45% of the time used on the more valuable acivities listed.

The 95% confidence interval for the intercept is from 0.383 to 0.521 and the interval for the slope is from -0.814 to -0.369. The confidence band is shown in the graph and represents 95% of the other models that could have been obtained with a different sample. Nicholas Taleb may now comment.

These are the diagnostic plots. An ordered values plot should not be necessary because the way the data was sampled.
```{r, message = FALSE}
par(mfrow = c(1,2))
plot(time_lm, which = 1, main = "Residuals vs Fitted")
qqPlot(time_lm$residuals, main = "QQ-Plot", ylab = "Residuals")
```
I can see from these plots that the variance is not constant and the residuals are not normally distributed. They seem to be a bit right skewed and possibly light-tailed. This means my model is not accurate. I could perform a new regression to better match the curvature, but I choose not to. :)